SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations

### 2015-08-19 paper.tex
changed figures

\begin{figure*}[ht]
\centering
\subfigure[Kernel Density Estimation of Sampled Data]{%
\vspace{-0.5ex}\includegraphics[width=5.5cm , height = 4.5cm]{figures/kde_gmm.eps}
\label{fig:subfigure1}}
\quad
\subfigure[One Class SVM]{%
\includegraphics[width=5.5cm, height = 4.5cm]{figures/kde_gmm_ocm.eps}
\label{fig:subfigure2}}
\subfigure[Risk Sensitive One Class SVM]{%
\includegraphics[width=5.5cm, height = 4.5cm]{figures/kde_gmm_mocm.eps}
\label{fig:subfigure3}}

@@

\begin{table}[t]
\centering
\begin{tabular}{ R{4cm}||R{1.65cm}|R{1.65cm}|R{1.65cm}  }
 %\hline
 %\multicolumn{4}{|c|}{Sensitivity Analysis for Convergence to Best Grasp for Thompson sampling} \\
 %\hline 
 & \multicolumn{1}{c}{Mis-Prediction Error} \\
 \hline
 Risk Sensitive One Class SVM &  $16 \pm 2\%$\\
Estimated Confidence & $59 \pm 3\%$\\
 %\hline
\end{tabular}
   \caption { \footnotesize  To compare our method against a traditional confidence based active learning approach, we use a confidence measure  of distance from the hyperplane. The threshold was set to the average distance from the hyperplane for the mis-classified points in $\mathcal{D}_0$, which consisted of two demonstrations from our solver. We measured the performance of our modified One Class SVM to the confidence measure, in terms of how many states are estimated to be of low risk (i.e. correctly classified) and are of actually high risk on the first policy roll out. Results  are averaged over 50 randomly generated tracks. 
   }
		\tablabel{opt-p-comparison}
\label{table:active_comp}
\end{table}

>>>>

\begin{figure*}[ht]
\centering

\includegraphics[width=16cm , height = 5cm]{figures/active_learning/Slide1.jpg}

@@

\begin{figure}[t]
\centering
\includegraphics[width=9cm, height=8cm]{figures/risk_bar.eps}
   \caption { \footnotesize  To compare our method against a traditional confidence based active learning approach, we use a confidence measure  of distance from the hyperplane. The threshold was set to the average distance from the hyperplane for the mis-classified points in $\mathcal{D}_0$, which consisted of two demonstrations from our solver. We measured the performance of our modified One Class SVM to the confidence measure, in terms of how many states are estimated to be of low risk (i.e. correctly classified) and are of actually high risk on the first policy roll out. Results  are averaged over 50 randomly generated tracks. 
   }

\label{fig:active_comp}
\end{figure}
